Evaluation of 3-point correlation functions from structural images on CPU and GPU architectures: accounting for anisotropy effects

### 2023-12-25 paper.tex
More images

\subsection{Applications to material images}
In this section we compute correlation functions for 2- and 3-dimensional real
samples. Table \ref{tab:summary} contains information about these samples. Note
that we compute surface correlation functions only for those samples for which
the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
of the samples are on \cref{fig:samples}. On plots of correlation functions for
isotropic samples we provide a family of curves with the first argument of the
correlation function being fixed. For anisotropic samples we provide heatmaps of
correlation functions where anisotropy can be easily observed.

@@

Heatmaps of $S_3$ for the two highly anisotropic samples can be seen on
\cref{fig:heatmaps}. Anisotropy of the both samples can be seen as a slower
decay of $S_3$ in one of the directions. Additionally, it can be observed that
elongated clusters of the void phase in the sample of soil are parallel to each
other and have a regular spacing of about $50 \mu m$.

\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table*}

\begin{figure*}[tp]
  \centering
  \subfigure[Sanstone XCT]{
    \includegraphics[width=0.4\linewidth]{images/15581.png}
    \label{fig:sample-sandstone-xct}}
  \hfill
  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \hfill
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil. $S_3$ function was clamped to the range $[0, 0.1]$ to make
    anisotropy more visible. It can be observed that the samples have
    cavities elongated along the vector $(1, 1, 0)$.}
  \label{fig:heatmaps}
\end{figure*}

>>>>

\subsection{Applications to material images}
\begin{table*}[!htp]
  \centering
  \begin{tabular}{|c|c|c|c|c|}
    \hline
    Sample name & Image type & Dimensions (pixels) & Image resolution ($\mu m$) & $C_{0.5}$\\
    \hline
    Sandstone & XCT &  $500 \times 500 \times 500$ & 2.25 & 0.9703 \\
    Soil & XCT & $160 \times 160 \times 160$ & 2.25 & 0.9210 \\
    Shale & XCT & $160 \times 160 \times 160$ & 2.25 & 0.8912 \\
    Sandstone & SEM &  $1280 \times 869$ & 0.10 & 0.9703 \\
    \hline
  \end{tabular}
  \caption{Summary of samples used for calculation of correlation functions.}
  \label{tab:summary}
\end{table*}
In this section we compute correlation functions for 2- and 3-dimensional real
samples. Table \ref{tab:summary} contains information about these samples. Note
that we compute surface correlation functions only for those samples for which
the criterion $C_{0.5} > 0.97$ holds (the two sandstones and the \textcolor{red}{shale}). Images
of the samples are on \cref{fig:samples}. On plots of correlation functions for
isotropic samples we provide a family of curves with the first argument of the
correlation function being fixed. For anisotropic samples we provide heatmaps of
correlation functions where anisotropy can be easily observed.
\begin{figure*}[tp]
  \centering
  \subfigure[Sanstone XCT]{
    \includegraphics[width=0.4\linewidth]{images/15581.png}
    \label{fig:sample-sandstone-xct}}
  \hfill
  \subfigure[Sandstone SEM (different clusters of void phase are shown in color)]{
    \includegraphics[width=0.4\linewidth, frame]{images/sandstone1.png}
    \label{fig:sample-sandstone}}
  \vskip\baselineskip
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil.png}
    \label{fig:sample-soil}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale.png}
    \label{fig:sample-shale}}
  \caption[]{Images of samples used for calculation of higher-order correlation
    functions.}
  \label{fig:samples}
\end{figure*}

@@

The anisotropic samples (the soil and the shale) were preliminarily rotated with
periodic boundary conditions to align elongated pores with coordinate axes. The
result of rotation can be seen on \cref{fig:samples-rot}. Heatmaps of $S_3$
function for these samples can be seen on \cref{fig:heatmaps}. It can be
observed that elongated clusters of the void phase in the sample of soil form a
structure which resembles a regular grid with spacing of about $60 \mu m$. The
sample of shale shows less regular yet still anisotropic structure.

@@

\begin{figure*}[tp]
  \centering
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil-rot.png}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale-rot.png}}
  \caption[]{Rotations of anisotropic samples with pores aligned with the
    coordinate axes.}
  \label{fig:samples-rot}
\end{figure*}

\begin{figure*}[tp]
  \centering
  \subfigure[Soil]{
    \includegraphics[width=0.4\linewidth]{images/soil-s3.png}
    \label{fig:soil-s3}}
  \hfill
  \subfigure[Shale]{
    \includegraphics[width=0.4\linewidth]{images/shale-s3.png}
    \label{fig:shale-s3}}
  \caption[]{Heatmaps of $S_3$ function for highly anisotropic samples of shale
    and soil.}
  \label{fig:heatmaps}
\end{figure*}
